---
title: " "
---

```{r echo = F, message = F, warning = F}
library(tidyverse)
library(knitr)
opts_chunk$set(echo = FALSE, warning = F, message = F)
```

<div style="text-align: right; font-size: .7em">
<FONT color="grey">Last update: `r lubridate::today()`  </FONT>
</div>

## Author

### Contact 

- Keach MURAKAMI (Ph.D.)  
    - mail: keach.murakami`r icon::fa_at()`gmail.com
    - CV: [`r icon::fa_file_alt()`](https://www.dropbox.com/sh/iifrhaxt3rauv0m/AACqpUHhxcXPIaoColJHmKLaa?preview=CV.pdf)

### Affiliation

2018.05--2019.02  
Chow laboratory, Research School of Biology, The Australian National University, Australia

2017.04--2020.03  
Graduate School of Sciences and Technology for Innovation, Yamaguchi University, Japan

### Education

```{r Education, echo = F}
data.frame(
  Year = c("2012.03", "2014.03", "2017.03"),
  Degree = c("B.S. in Agricultural Engineering, The University of Tokyo",
             "M.S. in Agricultural Engineering, The University of Tokyo",
             "Ph.D. in Agricultural Engineering, The University of Tokyo")
) %>%
  kable
```

---

## Research

### Speciality

- Environmental control in plant production systems
- Regulation of leaf/canopy photosynthesys

### Works

- [Publications](https://keachmurakami.github.io/page/publication_list/)
- [`r icon::ai("google-scholar", size=2)`](https://scholar.google.co.jp/citations?user=IgtMr-oAAAAJ&hl=en) / [`r icon::ai("orcid", size=2)`](https://orcid.org/0000-0001-8150-9535) / [`r icon::ai("researchgate", size=2)`](https://www.researchgate.net/profile/Keach_Murakami) 

### Professional Experience

```{r Professional_Experience, echo = F}
data.frame(
  Year = c("2014.04--2017.03", "2017.04--2020.03"),
  Category = c("JSPS Research Fellow (DC1)", "JSPS Postdoctoral Research Fellow (PD)"),
  Affiliation =
    c("Graduate School of Agricultural and Life Sciences, The University of Tokyo, Japan",
      "Graduate School of Sciences and Technology for Innovation, Yamaguchi University, Japan"),
  Advisor = c("Prof: Kazuhiro Fujiwara",
              "Prof: Yasuomi Ibaraki")
) %>%
  kable
```

### Grant

```{r grant, echo = F}
data.frame(
  Year = c("2014.04--2017.03", "2017.04--2020.03"),
  Title = c("Estimation of photosynthetic electron transport rate from light spectrum based on photochemical reactions at photosystems",
            "Development of a state-space model of leaf photosynthetic characteristics for prediction and regulation of whole-plant photosynthesis"),
  Category = c("Grant-in-Aid for JSPS Fellows (DC1)",
               "Grant-in-Aid for JSPS Fellows (PD)"),
  Budget = c("JPY 3,200,000", 
            "JPY 4,550,000"),
  URL = c("https://kaken.nii.ac.jp/en/grant/KAKENHI-PROJECT-14J09372/",
         "https://kaken.nii.ac.jp/en/grant/KAKENHI-PROJECT-17J04736/")
) %>%
  mutate(Title = paste0(Title, "<a href = '", URL, "' target='_blank'> (link)</a>")) %>%
  select(-URL) %>%
  kable
```

<div style="text-align: right; font-size: .7em">
\* <FONT color="grey">linked to KAKEN pages maintained by National Institute of Informatics (NII) of JAPAN.</FONT>
</div>

### Academic Society Membership

```{r Academic_Society_Membership, echo = F}
data.frame(
  Year = c("2012-", "2013-", "2017-", "2017-"),
  Society = c("Japanese Society of Agricultural, Biological and Environmental Engineers and Scientists",
              "The Society of Agricultural Meteorology of Japan",
              "The Japanese Association for Photosynthesis Research",
              "International Society for Horticultural Science")
) %>%
  kable
```

## Others

- Languages
    - Japanese > [`r icon::fa("r-project")`](https://www.r-project.org/) >> English
- Activities
    - `r icon::fa("futbol")`
    - `r icon::fa("bicycle")` (Fuji -> TREK)